Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex
Table
Experiments

\begin{table}[t!] 
  \centering\scriptsize
  \caption{Metrics for supervised learning with image data. SVGP is our method, and the number inside parentheses is the number of inducing points. SVGP NN is a modification of our method, where the mean is from the NN directly and the variance is from the GP model.} 
	\label{tbl:imagesuper}
	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{6pt}
	\setlength{\tblw}{0.095\textwidth}

@@

    % THE TABLE CAN BE FORMATTED MORE LIKE THIS
    % \begin{tabular}{l l C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
    % \toprule
    % & Method & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & OOD-AUC~$\uparrow$  \\
    % \midrule
    % \multirow{2}{*}{FMNIST}
    % & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % \midrule
    % \multirow{2}{*}{CIFAR-10}
    % & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % \bottomrule
    % \end{tabular}
  \newcommand{\myline}{\protect\tikz[baseline=-.5ex,line width=1pt]\protect\draw[draw=black!50](0,0)--(7em,0);}
  \begin{tabular}{l c C{\tblw} C{\tblw} C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
    \toprule
            &     &  \multicolumn{3}{c}{\myline~MNIST~\myline} & \multicolumn{3}{c}{\myline~FMNIST~\myline} \\
     Method & $M$ & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ \\
    \midrule
    %\multirow{2}{*}{MNIST}
    MAP & & \val{98.22}{0.13} & \val{0.061}{0.004} & \val{0.006}{0.001}
          & \val{91.39}{0.11} & \val{0.258}{0.004} & \val{0.017}{0.001} \\
    BNN predictive \cite{immer2021improving} & & \val{93.14}{0.05} & \val{0.304}{0.002} & \val{0.111}{0.003}
                                               & \val{84.42}{0.12} & \val{0.942}{0.016} & \val{0.411}{0.008} \\
    BNN predictive \cite{ritter2018kfac} & & \val{93.03}{0.13} & \val{0.369}{0.003} & \val{0.168}{0.001}
                                           & \val{91.20}{0.07} & \val{0.265}{0.004} & \val{0.024}{0.002} \\
    GLM predictive \cite{immer2021improving} & & \val{98.40}{0.05} & \val{0.054}{0.002} & \val{0.007}{0.001}
                                               & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\
    GP predictive \cite{immer2021improving} & $3200$ & \val{98.22}{0.13} & \val{0.058}{0.001} & \val{0.003}{0.000}
                                                     & \val{91.36}{0.11} & \val{0.25}{0.004} & \val{0.007}{0.001} \\

@@

Similarly to the UCI experiments, we seek to demonstrate \our on image data. We consider MNIST and Fashion-MNIST (FMNIST), and neural networks (CNN, architecture matches \cite{immer2021improving}) for the FMNIST and CIFAR10 classification tasks. After training, we computed the duals for NN2SVGP and used the resulting SVGP for uncertainty estimates, see \cref{tbl:imagesuper}. We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert]. We ran the experiment over $5$ seeds. During the NN training, we used a batch size of $512$ and an Adam optimizer with learning rate $1e-3$.

In addition to uncertainty estimates, our method can update the posterior when given new data. We gave the SVGP model 10 \% of the test dataset used for evaluation, and compare the performance of the SVGP model and the retrained NN in [INSERT TABLE].

>>>>

\begin{table}[t!] 
  \centering\scriptsize
  \caption{Metrics for supervised learning on image data with a CNN. We report accuracy, NLPD, and expected calibration error (mean$\pm$std) over 10 seeds. Our \our method is able to match the full methods using only a sparse set. For the GP predictive sparse subset method and \our we report results both using the NN MAP as mean (NN) and GP  mean.} 
	\label{tbl:imagesuper}
	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{6pt}
	\setlength{\tblw}{0.095\textwidth}

@@

    % THE TABLE CAN BE FORMATTED MORE LIKE THIS
    % \begin{tabular}{l l C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
    % \toprule
    % & Method & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & OOD-AUC~$\uparrow$  \\
    % \midrule
    % \multirow{2}{*}{FMNIST}
    % & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % \midrule
    % \multirow{2}{*}{CIFAR-10}
    % & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % \bottomrule
    % \end{tabular}
  \newcommand{\myline}{\protect\tikz[baseline=-.5ex,line width=.7pt]\protect\draw[draw=gray](0,0)--(7em,0);}
  \begin{tabular}{l c C{\tblw} C{\tblw} C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
    \toprule
            &     &  \multicolumn{3}{c}{\myline~MNIST~\myline} & \multicolumn{3}{c}{\myline~FMNIST~\myline} \\
     Method & $M$ & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ \\
    \midrule
    %\multirow{2}{*}{MNIST}
    MAP & & \val{98.22}{0.13} & \val{0.061}{0.004} & \val{0.006}{0.001}
          & \val{91.39}{0.11} & \val{0.258}{0.004} & \val{0.017}{0.001} \\
    BNN predictive \cite{immer2021improving} & & \val{93.14}{0.05} & \val{0.304}{0.002} & \val{0.111}{0.003}
                                               & \val{84.42}{0.12} & \val{0.942}{0.016} & \val{0.411}{0.008} \\
    BNN predictive \cite{ritter2018kfac} & & \val{93.03}{0.13} & \val{0.369}{0.003} & \val{0.168}{0.001}
                                           & \val{91.20}{0.07} & \val{0.265}{0.004} & \val{0.024}{0.002} \\
    GLM predictive \cite{immer2021improving} & & \val{98.40}{0.05} & \val{0.054}{0.002} & \val{0.007}{0.001}
                                               & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\
    GP predictive \cite{immer2021improving} & $3200$ & \val{98.22}{0.13} & \val{0.058}{0.001} & \val{0.003}{0.000}
                                                     & \val{91.36}{0.11} & \val{0.25}{0.004} & \val{0.007}{0.001} \\

@@

Similarly to the UCI experiments, we seek to demonstrate \our on image data that features more complicated data manifolds and model structures. We consider the MNIST and Fashion-MNIST (FMNIST) classification tasks, and use a CNN architecture (matching the setup in \cite{immer2021improving}). After training, we computed the duals for \our and use the model for prediction (full experiment details in \cref{app:image}). In \cref{tbl:imagesuper}, we compare to baselines also used in \cite{immer2021improving}. For \our and the GP predictive subset method by \cite{immer2021improving} we fix the number of points $M=1024$. For the baseline we additionally include a higher $M$ for comparison. We report accuracy (ACC), NLPD, and expected calibration error (ECE). The results in \cref{tbl:imagesuper} agree with the conclusions drawn from the UCI experiments showing that \our is able to more efficiently capture the posterior using a sparse set of points. These results on image data motivates, the experiments that follow that consider learning beyond the supervised learning setting. 
%We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert]. We ran the experiment over $5$ seeds. During the NN training, we used a batch size of $512$ and an Adam optimizer with learning rate $1e-3$.

%In addition to uncertainty estimates, our method can update the posterior when given new data. We gave the SVGP model 10 \% of the test dataset used for evaluation, and compare the performance of the SVGP model and the retrained NN in [INSERT TABLE].
